Bootstrap learning via modular concept discovery

### 2013-04-21 drafts/ijcai2013/ijcai13.tex
Edits based on reviewer comments.

A natural metric for the compressibility of a set of binary trees is
the number of unique subtrees (counting leaves) that this
set contains. As an example of this, suppose we have six tasks whose
solutions are integers $4^2, 5^2, 6^2, 7^2$, and $8^2$, and suppose our
frontier contains the $10$ expressions:
\vspace{-.3cm}
\captionsetup[subfigure]{labelformat=empty} 
\begin{figure}[h!]
   \begin{subfigure}{.17\linewidth}
     \begin{tikzpicture}[scale=.7, background rectangle/.style={fill=lightgray}] 
       \tikzset{level distance=15pt, sibling distance=10pt}
       \Tree [[  * 4 ] 4 ]
     \end{tikzpicture}
  \end{subfigure}
  \begin{subfigure}{.17\linewidth}
     \begin{tikzpicture}[scale=.7]
       \tikzset{level distance=15pt, sibling distance=10pt}
       \Tree [[  * 5 ] 5 ]
     \end{tikzpicture}
  \end{subfigure}
   \begin{subfigure}{.17\linewidth}
     \begin{tikzpicture} [scale=.7]
       \tikzset{level distance=15pt, sibling distance=10pt}
       \Tree [[  * 6 ] 6 ]
     \end{tikzpicture}
  \end{subfigure}
   \begin{subfigure}{.17\linewidth}
     \begin{tikzpicture}[scale=.7] 
       \tikzset{level distance=15pt, sibling distance=10pt}
       \Tree [[  * 7 ] 7 ]
     \end{tikzpicture}
  \end{subfigure}
  \begin{subfigure}{.17\linewidth}
     \begin{tikzpicture}[scale=.7] 
       \tikzset{level distance=15pt, sibling distance=10pt}
       \Tree [[  * 8 ] 8 ]
     \end{tikzpicture}
  \end{subfigure}
  \vspace{2mm}

@@

\setcounter{subfigure}{0} 
\begin{figure}[ht]
\centering
\includegraphics[width=1.0\linewidth]{figures/symreg3frontiers.pdf}
\vspace{-.2cm}
\caption{Learning curves as a function of frontier size.  As frontier
  size is increased, curves plateau closer to $100\%$ performance. A
  baseline search over $150000$ expressions only hits $3\%$ of the
  tasks. \label{fig:symregLearning}}
\vspace{-.3cm}
\end{figure}
\begin{figure}[ht]
\includegraphics[width=1.07\linewidth]{figures/symRegDiffCurricula.pdf}
\caption{How do different task sets affect learning curves? Learning
  curves at frontier size of $10000$ for different task
  sets.} 
\label{fig:symregCurricula}

>>>>

A natural metric for the compressibility of a set of binary trees is
the number of unique subtrees (counting leaves) that this set
contains. More sophisticated metrics exist; we could use the negative
logarithm of the probability of the solutions under a suitable
probability distribution~\cite{DBLP:journals/tit/BarronRY98}. Future
work will explore whether this sophistication is worthwhile and which
prior on grammars makes sense. For our purposes here, the unique
subtree counting metric appropriately rewards reuse of useful
subtrees. As an example of this, suppose we have six tasks whose
solutions are integers $4^2, 5^2, 6^2, 7^2$, and $8^2$, and suppose
our frontier contains the $10$ expressions:
\vspace{-.3cm}
\captionsetup[subfigure]{labelformat=empty} 
\begin{figure}[h!]
   \begin{subfigure}{.17\linewidth}
     \begin{tikzpicture}[scale=.7, background rectangle/.style={fill=lightgray}] 
       \tikzset{level distance=15pt, sibling distance=10pt}
       \Tree [[  * 4 ] 4 ]
     \end{tikzpicture}
  \end{subfigure}
  \begin{subfigure}{.17\linewidth}
     \begin{tikzpicture}[scale=.7]
       \tikzset{level distance=15pt, sibling distance=10pt}
       \Tree [[  * 5 ] 5 ]
     \end{tikzpicture}
  \end{subfigure}
   \begin{subfigure}{.17\linewidth}
     \begin{tikzpicture} [scale=.7]
       \tikzset{level distance=15pt, sibling distance=10pt}
       \Tree [[  * 6 ] 6 ]
     \end{tikzpicture}
  \end{subfigure}
   \begin{subfigure}{.17\linewidth}
     \begin{tikzpicture}[scale=.7] 
       \tikzset{level distance=15pt, sibling distance=10pt}
       \Tree [[  * 7 ] 7 ]
     \end{tikzpicture}
  \end{subfigure}
  \begin{subfigure}{.17\linewidth}
     \begin{tikzpicture}[scale=.7] 
       \tikzset{level distance=15pt, sibling distance=10pt}
       \Tree [[  * 8 ] 8 ]
     \end{tikzpicture}
  \end{subfigure}
  \vspace{2mm}

@@

\setcounter{subfigure}{0} 
\begin{figure}[ht]
\centering
\includegraphics[width=1.0\linewidth]{figures/symreg3frontiers.pdf}
\vspace{-.2cm}
\caption{Learning curves as a function of frontier size.  As frontier
  size is increased, curves plateau closer to $100\%$ performance. A
  baseline search over $150000$ expressions only hits $3\%$ of the
  tasks (dashed pink line). \label{fig:symregLearning}}
\vspace{-.3cm}
\end{figure}
\begin{figure}[ht]
\includegraphics[width=1.07\linewidth]{figures/symRegDiffCurricula.pdf}
\caption{How do different task sets affect learning curves? Learning
  curves at frontier size of $10000$ for different task
  sets.} 
\label{fig:symregCurricula}
